\section{Collected statistics}\label{sec:statistics}

All \code{@statistic} are defined in the \code{Floorplan} network's NED file and
they are collected using the \omnetpp{} signaling system by the \code{Oracle}
and the \code{User} modules.

The following statistics are collected by the \code{Oracle} module and are
related to the entire \code{Floorplan} network:
\begin{description}
	\item[activityTime] When a user perform some ``activity'' \idest{receive
		or send a message, excluding self messages} the Oracle signals
		the simulation time of the event. The last value signaled is
		recorded and represents the total broadcast time (regardless of
		whether all users have been reached or not).
	\item[coveredUsers] The number of users infected \idest{those who
		successfully heard the message}. A value with timestamp is
		recorded in each slot along with the sum of all values (the
		total number of infected users at the end of the simulation).
		This also allows us to compute percentiles of network coverage
		by processing vectorial data.
	\item[msgsPerSlot] For each slot, the number of users who sent out
		the message. Histogram and general statistics \idest{mean,
		stddev, min, max, sum, \etc} are also recorded.
\end{description}

The following statistics are collected by the \code{User} module and are mainly
related to the single user in the simulation:
\begin{description}
	\item[collisions] The number of collisions registered by the user.
		Histogram and general statistics are collected along with the
		sum of all collisions in the entire network.
	\item[totalCollisions] The number of colliding messages registered by
		the user in each slot \exgratia{If a user receives three copies
		of the same message they count as 3 total collisions}. Also
		histogram and the total sum of the network are collected.
	\item[copies] The number of copies of the message successfully heard by
		the user during the time window between the reception of the
		message and the time at which the user relays it. Histogram and
		general statistics are collected.
	\item[reachedUsers] When a user relays the message, it signals the
		number of users reached (regardless of whether they correctly
		hear the message or not). Values for each message sent,
		histogram and general statistics are collected.
\end{description}
