\chapter{Data analysis}\label{ch:analysis}

To perform the analysis of the three scenarios we have prepared a shell
script\footnote{\code{simulations/simulate.sh}.} that executes parallel runs
with the configuration specified by a command line parameter and exports the
results inside a specified folder in the \code{analysis/} directory in CSV
format.

The \code{analysis/} directory contains various Jupyter notebook used to analyze
the data. Those notebooks have been developed with automation in mind: we just
need to configure it in the ``Config'' section at the start of the notebook and
run it. Python will then output a complete analysis on the provided data. This
means that, often, not all the plots/tables created by these scripts are really
useful for the analysis (they are plotted, but this does not mean they are
meaningful in every situation). Moreover, when we need to run the same Jupyter
notebook with different configuration parameters \exgratia{to apply or not a
transformation on the predicted variable in the 2\textsuperscript{k}r assumption
verification} we will just copy and paste the notebook and change the needed
configuration parameters.

The \code{analysis/} folder contains ``generic'' Jupyter notebooks that we will
copy inside some other folder before run it for a specific scenario. So, for
example, analysis for the ``High density scenario'' can be found inside the
\code{analysis/HighDensity} folder.

For each Jupyter notebook execution we have also saved the output in HTML
format. So, as an example, for the ``High density scenario'', inside the
\code{analysis/HighDensity/exported\_html/} you can found the output of each
Jupyter notebook of the \code{analysis/HighDensity/} directory. This may be
useful to inspect the results of our analysis even if Jupyter is not installed.

In the following we will discuss the most important considerations on the
results provided by Python. In any case, we will ofter refer to the Jupyter
notebook file which contains the full analysis. So, for example, if in the
``High density scenario'' we mention the \code{2kr.ipynb} file, head to the
\code{analysis/HighDensity/2kr.ipynb} file to read the full analysis (or the
equivalent HTML exported version inside the \code{exported\_html/} sub-folder).

\input{scenarios/high-density}
\input{scenarios/low-density}
\input{scenarios/rectangular}
